Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-30 paper.tex
update

\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
      and significantly expanded within the stratified atmosphere afterwards.\
      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      %in which CRs could increase the compressibility of the fluid,\
      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
      The similarity of the morphology, temperature, and gamma-ray spectrum between\
      simulated and observed bubbles suggests that\
      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium. The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced. The best-fit\
      CRe power-law index is found to be 2.4.
\item Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe,
      possibly in balance with the IC and synchrotron cooling.\
      We will investigate the competition between stochastic acceleration and radiative cooling
      in a future work.
      {\color{red} KY: This item is to be modified according to the newly added text in the Discussion section.}
\end{itemize}

>>>>

\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
      and significantly expanded within the stratified atmosphere afterwards.\
      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      %in which CRs could increase the compressibility of the fluid,\
      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
      The similarity of the morphology, temperature, and gamma-ray spectrum between\
      simulated and observed bubbles suggests that\
      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium. The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced. The best-fit\
      CRe power-law index is found to be 2.4.
\item The elapsed time of 12.39 Myr required for the simulated bubbles
      to reach the desired morphology
      is ten times longer than the typical synchrotron and IC cooling time scale of
      high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe must be considered
      in this model. As opposed to shock acceleration,
      the acceleration of CRe that can compete with IC and synchrotron cooling
      may be dominated by the stochastic acceleration associated with the Galactic magnetic field,
      since the forward shock is rather far away from the gamma-ray bubbles.
      We will investigate the competition between stochastic acceleration and radiative cooling
      in a future work.
      {\color{red} KY: This item is to be modified according to the newly added text in the Discussion section.}
\end{itemize}
